Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-27 paper/paper.tex
On the last epoch

\subsection{Upper bound.}
Now we give an algorithm for a restricted variant of  \OBRP{}, named \PPOBRP{},
%\maciek{This is not sufficient! We also disallow serving requests remotely.}
where an optimal offline algorithm ($\OPT$) moves to a perfect partition
at the beginning and stays there perpetually.
%We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to recover (or learn) the perfect partition while not paying too much relative to \OPT.
%
%\maciek{This is not a valid description of the model. We need the assumption that collocation is needed in our model. Otherwise OPT would just serve some requests remotely, and our analysis would not hold.}
The first request between any two non-collocated nodes reveals an edge of the communication graph.
Our online algorithm collocates them immediately and never separates them since by assumption \OPT does the same.
Revealed edges, up to any point in the sequence,
induce some connected subgraphs which grow as components.
%An algorithm that always  keeps nodes belonging to the same component collocated is \emph{component respecting}.

@@

@@

%\maciek{Shouldn't we think about whole component cuts instead of single edge? Hmm. NO!}

@@

  It remains to consider the last, unfinished phase.
  Consider the case, where the unfinished phase is also the first one.
  Then, we cannot charge $\OPT$ due to the inability to partition the components.
  Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
  We charge $\OPT$ $\alpha$ for the first external $\alpha$ requests or a migration,
  and we follow the analysis regarding the unsaturated requests.
  If the input finished before the first $\alpha$ external requests, then \TAlg is optimal.
  Now, consider the case, where there are at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests.
  This way, the competitive ratio increases at most twofold.
\end{proof}

>>>>

\subsection{Upper bound.}
Now we give an algorithm for a restricthed variant of  \OBRP{}, named \PPOBRP{},
%\maciek{This is not sufficient! We also disallow serving requests remotely.}
where an optimal offline algorithm ($\OPT$) moves to a perfect partition
at the beginning and stays there perpetually.
%We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to recover (or learn) the perfect partition while not paying too much relative to \OPT.
%
%\maciek{This is not a valid description of the model. We need the assumption that collocation is needed in our model. Otherwise OPT would just serve some requests remotely, and our analysis would not hold.}
The first request between any two non-collocated nodes reveals an edge of the communication graph.
Our online algorithm collocates them immediately and never separates them since by assumption \OPT does the same.
Revealed edges, up to any point in the sequence,
induce some connected subgraphs which grow as components.
%An algorithm that always  keeps nodes belonging to the same component collocated is \emph{component respecting}.

@@

\maciek{REALLY bad name. Both the learning problem and the general one is online.}

@@

@@

  \maciek{Big techincal TODO. Formalize the sketched proof for the last phase.}
  It remains to consider the last, unfinished phase.
  Consider the case, where the unfinished phase is also the first one.
  Then, we cannot charge $\OPT$ due to the inability to partition the components.
  Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
  We charge $\OPT$ $\alpha$ for the first external $\alpha$ requests or a migration,
  and we follow the analysis regarding the unsaturated requests.
  If the input finished before the first $\alpha$ external requests, then \TAlg is optimal.
  Now, consider the case, where there are at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests.
  This way, the competitive ratio increases at most twofold.
\end{proof}
